Lightweight Ruby Framework for Improving Embedded Software Efficiency

### 2016-10-20 CPSNA2016/enago/paper.tex
adjust

In the future, CDL files for the RiteVM and mruby-TECS bridge will be generated automatically using a plugin.
% and developers will be able to transfer bytecodes using the ZMODEM protocol on the command line.
Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.

%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Acknowledgement}
% This work was supported by JSPS KAKENHI Grant Number 15H05305.
% We thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtranBST2/IEEEtran}
\bibliography{ref}

\clearpage
\appendices
\section{mruby}
\label{apn:mruby}
mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[b]
    \centering
    \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
    \vspace{-3mm}
    \caption{mruby/RiteVM mechanism}
    \vspace{-3mm}
    \label{fig:mruby}
\end{figure}

\section{TECS}
\label{apn:TECS}
TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

In TECS, component deployment and composition are performed statically.
Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.

\begin{figure}[b]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    \vspace{-2mm}
    \caption{Component Diagram}
    \vspace{-5mm}
    \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Figure \ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.

\subsubsection{Component Description}
In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
% TECS code is written in CDL (component description language) file.
These components are described as follows.

% \begin{description}
    %\item[
    {\bf Signature Description:\ }%]\mbox{}\\
        {\it Signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.

    %\item[
    {\bf Celltype Description:\ }%]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.

    %\item[
    {\bf Build Description:\ }%]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[H]
\centering
\begin{lstlisting}
signature sMotor {
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Signature Description}
    \vspace{-5mm}
\label{signature}
\end{figure}

\begin{figure}[H]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Celltype Description}
    \vspace{-5mm}
\label{celltype}
\end{figure}

\begin{figure}[H]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Build Description}
    \vspace{-2mm}
\label{build}
\end{figure}
% \section{mruby on TECS}
% \subsection{System Model}
% The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
% Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
% TECS components support various embedded drivers such as motor and sensor drivers.
%
% An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
% The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
% mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
%
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
%     \vspace{-2mm}
% \caption{System model of existing mruby on TECS}
%     \vspace{-2mm}
% \label{fig:mrubyontecs}
% \end{figure}
%
% \subsection{mruby-TECS Bridge}
% There is a significant difference between the execution times of mruby and C language codes.
% According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
% Thus, it is difficult to use mruby exclusively.
%
% Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
% However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
% % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
%
% Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
% The left side of BridgeMotor belongs to the mruby program.
% The right side of BridgeMotor belongs to TECS component.
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
%     \vspace{-2mm}
% \caption{mruby-TECS bridge}
%     \vspace{-2mm}
% \label{fig:mruby_TECS_bridge}
% \end{figure}
%
% The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
%
% The generated mruby-TECS bridge supports registration of classes and methods for mruby.
% Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
% Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
%
\end{document}

>>>>

In the future, CDL files for the RiteVM and mruby-TECS bridge will be generated automatically using a plugin.
% and developers will be able to transfer bytecodes using the ZMODEM protocol on the command line.
Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.
% %%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % \section*{Acknowledgement}
% % This work was supported by JSPS KAKENHI Grant Number 15H05305.
% % We thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
% %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \bibliographystyle{IEEEtranBST2/IEEEtran}
% \bibliography{ref}
% \clearpage
% \appendices
% \section{mruby}
% \label{apn:mruby}
% Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
% \begin{figure}[b]
%     \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
%     \vspace{-3mm}
%     \vspace{-3mm}
% \section{TECS}
% \label{apn:TECS}
% \begin{figure}[b]
%     \vspace{-2mm}
%     \vspace{-5mm}
% % \begin{description}
%     %\item[
%     {\bf Signature Description:\ }%]\mbox{}\\
%         {\it Signature} defines a {\it cell} interface.
%     %\item[
%     {\bf Celltype Description:\ }%]\mbox{}\\
%     %\item[
%     {\bf Build Description:\ }%]\mbox{}\\
% % \end{description} 
% \begin{figure}[H]
%     \vspace{-2mm}
%     \vspace{-5mm}
% \begin{figure}[H]
%     \vspace{-2mm}
%     \vspace{-5mm}
% \begin{figure}[H]
%     \vspace{-2mm}
%     \vspace{-2mm}
% % \section{mruby on TECS}
% % \subsection{System Model}
% % The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
% % Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
% % TECS components support various embedded drivers such as motor and sensor drivers.
% %
% % An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
% % The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% % % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
% % mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
% %
% % \begin{figure}[t]
% %     \centering
% %     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
% %     \vspace{-2mm}
% % \caption{System model of existing mruby on TECS}
% %     \vspace{-2mm}
% % \label{fig:mrubyontecs}
% % \end{figure}
% %
% % \subsection{mruby-TECS Bridge}
% % There is a significant difference between the execution times of mruby and C language codes.
% % According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
% % Thus, it is difficult to use mruby exclusively.
% %
% % Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
% % However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
% % % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
% %
% % Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
% % The left side of BridgeMotor belongs to the mruby program.
% % The right side of BridgeMotor belongs to TECS component.
% % \begin{figure}[t]
% %     \centering
% %     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
% %     \vspace{-2mm}
% % \caption{mruby-TECS bridge}
% %     \vspace{-2mm}
% % \label{fig:mruby_TECS_bridge}
% % \end{figure}
% %
% % The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
% %
% % The generated mruby-TECS bridge supports registration of classes and methods for mruby.
% % Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
% % Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
% %
\end{document}

### 2016-10-20 CPSNA2016/paper.tex
adjust

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
    % \vspace{-2mm}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
% The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD.}
The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a sheduler, and Eventflags).
    % \vspace{-2mm}
\end{enumerate}

{\bf Organization}: The reminder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model, and Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

\section{System Model}
\label{sec:System Model}
The proposed framework is an extended framework of mruby on TECS\footnote{mruby on TECS is explained in detail in \cite{par:mrubyonTECS}}, and utilizes mruby and TECS.
mruby and TECS are described in Appendixes \ref{apn:mruby} and \ref{apn:TECS}.

>>>>

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
    % \vspace{-2mm}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
% The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a scheduler, and Eventflags).
    % \vspace{-2mm}
\end{enumerate}

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model, and Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

\section{System Model}
\label{sec:System Model}
The proposed framework is an extension of mruby on TECS\footnote{mruby on TECS is explained in detail in \cite{par:mrubyonTECS}}, and utilizes mruby and TECS, which are described in Appendices \ref{apn:mruby} and \ref{apn:TECS}.

### 2016-10-20 CPSNA2016/short_paper.tex
adjust

%
% File: paper.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference]{IEEEtran/IEEEtran/IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
    % \vspace{-2mm}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
% The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a sheduler, and Eventflags).
    % \vspace{-2mm}
\end{enumerate}

@@

\section{System Model}
\label{sec:System Model}
The proposed framework is an extension of mruby on TECS \cite{par:mrubyonTECS}, and utilizes mruby and TECS, which are also described in \cite{par:mrubyonTECS}.

@@

\section{Related Work}
\label{sec:Related work}
Open-source runtime systems for scripting languages have been proposed such python-on-a-chip \cite{url:python-on-a-chip}, Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

{\bf python-on-a-chip:} python-on-a-chip (p14p) is a Python runtime system that uses a reduced Python VM called PyMite.
The VM runs a significant subset of the Python language with few resources on a microcontroller.
p14p can also run multiple stackless green threads.

{\bf Owl system:} The Owl system is an embedded Python runtime system.
It is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images that are directly runnable on the microcontroller from Python code objects.
Note that the Owl system interpreter is the same as that of python-on-a-chip.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper presents an extended framework of mruby on TECS, i.e., the proposed framework implements a Bluetooth loader for mruby bytecode and a RiteVM scheduler.
The Bluetooth loader improves software development efficiency by eliminating the need to rewrite a storage/ROM device and restart an RTOS.
The proposed framework can be applied to various embedded systems because the loader can use both Bluetooth and a wired serial connection.
%Thus, the proposed framework can be utilized on the devices without Bluetooth.
The RiteVM scheduler simplifies multitasking compared to the current mruby on TECS.
Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is more effective than the existing technique and co-routines for multitasking.
Moreover, synchronization of multiple RiteVM tasks is implemented in the proposed framework.

@@

%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Acknowledgement}
% This work was supported by JSPS KAKENHI Grant Number 15H05305.
% We thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtranBST2/IEEEtran}
\bibliography{ref}

>>>>

%
% File: paper.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
%\documentclass[10pt, conference, compsocconf]{IEEEtran/IEEEtran}
\documentclass[10pt, conference]{IEEEtran/IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
    % \vspace{-2mm}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
% The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a scheduler, and Eventflags).
    % \vspace{-2mm}
\end{enumerate}

@@

\section{System Model}
\label{sec:System Model}
The proposed framework is an extension of mruby on TECS \cite{par:mrubyonTECS}, and utilizes mruby and TECS\footnote{mruby, TECS, and mruby on TECS are described in detail in \cite{par:mrubyonTECS}}.

@@

\section{Related Work}
\label{sec:Related work}
Open-source runtime systems for scripting languages have been proposed such p14p \cite{url:python-on-a-chip}, Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

{\bf p14p:} p14p is a Python runtime system that uses a reduced Python VM called PyMite.
The VM runs a significant subset of the Python language with few resources on a microcontroller.
p14p can also run multiple stackless green threads.

{\bf Owl system:} The Owl system is an embedded Python runtime system.
It is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images that are directly runnable on the microcontroller from Python code objects.
Note that the Owl system interpreter is the same as that of p14p.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper presents an extended framework of mruby on TECS, i.e., the proposed framework implements a Bluetooth loader for mruby bytecode and a RiteVM scheduler.
The Bluetooth loader improves software development efficiency by eliminating the need to rewrite a storage/ROM device and restart an RTOS.
The proposed framework can be applied to various embedded systems because the loader can use both Bluetooth and a wired serial connection.
%Thus, the proposed framework can be utilized on the devices without Bluetooth.
The RiteVM scheduler simplifies multitasking compared to the current mruby on TECS.
Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is more effective than the existing technique and co-routines for multitasking.
% Moreover, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
Moreover, multiple RiteVM tasks are synchronized.

@@

%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgement}
This work was supported by JSPS KAKENHI Grant Number 15H05305.
% We thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
\vspace{-3mm}
%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran/IEEEtranBST/IEEEtran}
\bibliography{ref}
